### 2013-07-27 doc/taxize_withcode_appA.tex
incorporated changes from karthik and naim, fixes #170, should be close to submit

\documentclass[letterpaper,superscriptaddress,showkeys,longbibliography,10pt]{revtex4-1}\usepackage{graphicx, color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

@@

\usepackage{alltt}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\usepackage[titletoc, title]{appendix}
\hypersetup
{
colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

@@

\begin{appendices}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# The tnrs function accepts a vector of 1 or more}
splist_tnrs <- \hlfunctioncall{tnrs}(query = splist, getpost = \hlstring{"POST"}, source_ = \hlstring{"iPlant_TNRS"})

\hlcomment{# Remove some fields}
(splist_tnrs <- splist_tnrs[, !\hlfunctioncall{names}(splist_tnrs) %in% \hlfunctioncall{c}(\hlstring{"matchedName"}, \hlstring{"annotations"}, 
    \hlstring{"uri"})])
\end{alltt}
\begin{verbatim}
           submittedName         acceptedName    sourceId score
3       Helanthus annuus    Helianthus annuus iPlant_TNRS  0.98
1         Pinos contorta       Pinus contorta iPlant_TNRS  0.96
4  Collomia grandiflorra Collomia grandiflora iPlant_TNRS  0.99
5       Abies magnificaa      Abies magnifica iPlant_TNRS  0.98
10       Rosa california     Rosa californica iPlant_TNRS  0.99
9         Datura wrighti      Datura wrightii iPlant_TNRS  0.98
7       Mimulus bicolour      Mimulus bicolor iPlant_TNRS  0.98
8       Nicotiana glauca     Nicotiana glauca iPlant_TNRS  1.00
6          Maddia sativa         Madia sativa iPlant_TNRS  0.97
2    Bartlettia scapposa   Bartlettia scaposa iPlant_TNRS  0.98
\end{verbatim}
\begin{alltt}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
tsns <- \hlfunctioncall{get_tsn}(searchterm = splist, searchtype = \hlstring{"sciname"}, verbose = FALSE)
comnames <- \hlfunctioncall{lapply}(tsns, getcommonnamesfromtsn)

\hlcomment{# Unfortunately, common names are not standardized like species names, so}
\hlcomment{# there are multiple common names for each taxon}
\hlfunctioncall{sapply}(comnames, length)
\end{alltt}
\begin{verbatim}
 [1] 3 3 3 3 3 3 3 3 3 3
\end{verbatim}
\begin{alltt}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# As we already have Taxonomic Serial Numbers from ITIS, let's just get}
\hlcomment{# classifications from ITIS. Note that we could use uBio instead.}
class_list <- \hlfunctioncall{classification}(tsns)
\hlfunctioncall{sapply}(class_list, nrow)
\end{alltt}
\begin{verbatim}
 [1] 12 11 12 11 12 12 12 12 12 12
\end{verbatim}
\begin{alltt}

@@

\begin{figure}[!h] 
\centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# Fetch phylogeny from phylomatic}
phylogeny <- \hlfunctioncall{phylomatic_tree}(taxa = \hlfunctioncall{as.character}(allnames$spname), taxnames = TRUE, 
    get = \hlstring{"POST"}, informat = \hlstring{"newick"}, method = \hlstring{"phylomatic"}, storedtree = \hlstring{"R20120829"}, 
    taxaformat = \hlstring{"slashpath"}, outformat = \hlstring{"newick"}, clean = \hlstring{"true"}, parallel = TRUE)
\hlcomment{# Format teeth-labels}
phylogeny$tip.label <- \hlfunctioncall{capwords}(phylogeny$tip.label, onlyfirst = TRUE)
\hlcomment{# plot phylogeny}
\hlfunctioncall{plot}(phylogeny)
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=4in,height=4in]{figure/phylogeny}

}

@@

\hlcomment{# Make a map}
p <- \hlfunctioncall{gbifmap}(occurr_list) + \hlfunctioncall{guides}(col = \hlfunctioncall{guide_legend}(title = \hlstring{""}, nrow = 3, 
    byrow = TRUE)) + \hlfunctioncall{theme}(legend.position = \hlstring{"bottom"}, legend.key = \hlfunctioncall{element_blank}()) + 
    \hlfunctioncall{coord_equal}()
p
\end{alltt}
\end{kframe}\begin{figure}[h]

{\centering \includegraphics[width=.9\textwidth]{figure/plot_map}

}

\caption[A map]{A map\label{fig:mapplot_map}}
\end{figure}

\newpage

\section{Matching species tables with different taxonomic resolution}

Trait-based approaches are a promising tool in ecology. Unlike taxonomy-based methods, traits may not be constrained to biogeographic boundaries \citep{baird_toward_2011} and have potential to disentangle the effects of multiple stressors \citep{statzner_can_2010}.

To analyse trait-composition abundance data must be matched with trait databases like \citet{usseglio-polatera_biological_2000}. However these two datatables may contain species information on different taxonomic levels and perhaps data must be aggregated to a joint taxonomic level.

taxize can help in this data-cleaning step, providing a reproducible workflow. Here we illustrate this on a small fictitious example.

Suppose we have fuzzy coded trait table with 2 traits with 3 respectively 2 modalities:
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
(traits <- \hlfunctioncall{read.table}(header = TRUE, sep = \hlstring{';'}, stringsAsFactors=FALSE, 
                      text = 'taxon;T1M1;T1M2;T1M3;T2M1;T2M2
Gammarus sp.;0;0;3;1;3
Potamopyrgus antipodarum;1;0;3;1;3
Coenagrion sp.;3;0;1;3;1
Enallagma cyathigerum;0;3;1;0;3
Erythromma sp.;0;0;3;3;1
Baetis sp.;0;0;0;0;0
'))
\end{alltt}
\begin{verbatim}
                     taxon T1M1 T1M2 T1M3 T2M1 T2M2
1             Gammarus sp.    0    0    3    1    3
2 Potamopyrgus antipodarum    1    0    3    1    3
3           Coenagrion sp.    3    0    1    3    1
4    Enallagma cyathigerum    0    3    1    0    3
5           Erythromma sp.    0    0    3    3    1
6               Baetis sp.    0    0    0    0    0
\end{verbatim}
\end{kframe}
\end{knitrout}

And want to match this to a table with abundances:
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
(abundances <- \hlfunctioncall{read.table}(header = TRUE, sep = \hlstring{';'}, stringsAsFactors=FALSE, 
                          text = 'taxon;abundance;sample
Gammarus roeseli;5;1
Gammarus roeseli;6;2
Gammarus tigrinus;7;1
Gammarus tigrinus;8;2
Coenagrionidae;10;1
Coenagrionidae;6;2
Potamopyrgus antipodarum;10;1
xxxxx;10;2
'))
\end{alltt}
\begin{verbatim}
                     taxon abundance sample
1         Gammarus roeseli         5      1
2         Gammarus roeseli         6      2
3        Gammarus tigrinus         7      1
4        Gammarus tigrinus         8      2
5           Coenagrionidae        10      1
6           Coenagrionidae         6      2
7 Potamopyrgus antipodarum        10      1
8                    xxxxx        10      2
\end{verbatim}
\end{kframe}
\end{knitrout}

First we do some basic data-cleaning and create a lookup-table, that will link taxa in trait table with the abundance table.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# first we remove ' sp.' from out trait table:}
traits$taxon_cleaned <- \hlfunctioncall{tolower}(\hlfunctioncall{gsub}(\hlstring{" sp."}, \hlstring{""}, traits$taxon))

\hlcomment{# since abundance tables can be very long with repeating taxa, we look}
\hlcomment{# only at unique taxon names This will be a lookup-table linking taxon}
\hlcomment{# names between both tables}
lookup <- \hlfunctioncall{data.frame}(taxon = \hlfunctioncall{tolower}(\hlfunctioncall{unique}(abundances$taxon)), stringsAsFactors = FALSE)
\end{alltt}
\end{kframe}
\end{knitrout}

The we query the taxonomic hierarchy for both tables, this will be the backbone of this procedure:
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlfunctioncall{require}(taxize)
traits_classi <- \hlfunctioncall{classification}(\hlfunctioncall{get_uid}(traits$taxon_cleaned))
lookup_classi <- \hlfunctioncall{classification}(\hlfunctioncall{get_uid}(lookup$taxon))
\end{alltt}
\end{kframe}
\end{knitrout}

First we look if we can find any direct matches between taxon names:
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# first search for direct matches}
direct <- \hlfunctioncall{match}(lookup$taxon, traits$taxon_cleaned)
\hlcomment{# and add the matched name to our lookup table}
lookup$traits <- \hlfunctioncall{tolower}(traits$taxon[direct])
lookup$match <- \hlfunctioncall{ifelse}(!\hlfunctioncall{is.na}(direct), \hlstring{"direct"}, NA)
lookup
\end{alltt}
\begin{verbatim}
                     taxon                   traits  match
1         gammarus roeseli                     <NA>   <NA>
2        gammarus tigrinus                     <NA>   <NA>
3           coenagrionidae                     <NA>   <NA>
4 potamopyrgus antipodarum potamopyrgus antipodarum direct
5                    xxxxx                     <NA>   <NA>
\end{verbatim}
\end{kframe}
\end{knitrout}

We found a direct match - \emph{potamopyrgus antipodarum} - so nothing to do here.

Next we look for species which are on a higher taxonomic resolution than our trait table. 
For these species we will take directly the trait-data since no better information is available.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# look for cases where taxonomic resolution in abundance data is higher}
\hlcomment{# than in trait data: here we take the trait-values for the lower}
\hlcomment{# resolution}
\hlfunctioncall{for} (i in \hlfunctioncall{which}(\hlfunctioncall{is.na}(lookup$traits))) \{
    \hlfunctioncall{if} (\hlfunctioncall{is.data.frame}(lookup_classi[[i]])) \{
        matches <- \hlfunctioncall{tolower}(lookup_classi[[i]]$ScientificName) %in% traits$taxon_cleaned
        \hlfunctioncall{if} (\hlfunctioncall{any}(matches)) \{
            lookup$traits[i] <- \hlfunctioncall{tolower}(lookup_classi[[i]]$ScientificName[matches])
            lookup$match[i] <- lookup_classi[[i]]$Rank[matches]
        \}
    \}
\}
lookup
\end{alltt}
\begin{verbatim}
                     taxon                   traits  match
1         gammarus roeseli                 gammarus  genus
2        gammarus tigrinus                 gammarus  genus
3           coenagrionidae                     <NA>   <NA>
4 potamopyrgus antipodarum potamopyrgus antipodarum direct
5                    xxxxx                     <NA>   <NA>
\end{verbatim}
\end{kframe}
\end{knitrout}

So our abundance data has two Gammarus species, however trait data is only on genus level.

The next step is to search for species were we have to aggregate trait-data, since our abundance data is on a lower taxonomic level.
We are walking the taxonomic latter for the species in our trait-data upwards and search for matches with out abundance data. Since we'll have many taxa in the trait-data belonging to one taxon, we'll take the median modality scores as an approximation. Of course also other methods may be used here, e.g. weighting by genetic distance.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# look for cases taxonomic resolution in abundance data is lower than in}
\hlcomment{# trait data, here we need to aggregate the trait-values (eg. median value}
\hlcomment{# for modality)}

\hlfunctioncall{for} (i in \hlfunctioncall{which}(\hlfunctioncall{is.na}(lookup$traits))) \{
\hlcomment{    # find matches}
    agg <- \hlfunctioncall{sapply}(traits_classi, \hlfunctioncall{function}(x) \hlfunctioncall{any}(\hlfunctioncall{tolower}(x$ScientificName) %in% 
        lookup$taxon[i]))
    \hlfunctioncall{if} (\hlfunctioncall{sum}(agg) > 1) \{
\hlcomment{        # add taxon as aggregate to trait-table}
        traits <- \hlfunctioncall{rbind}(traits, \hlfunctioncall{c}(\hlfunctioncall{paste0}(lookup$taxon[i], \hlstring{"-aggregated"}), \hlfunctioncall{apply}(traits[agg, 
            2:6], 2, median), \hlfunctioncall{paste0}(lookup$taxon[i], \hlstring{"-aggregated"})))
\hlcomment{        # fill lookup table}
        lookup$traits[i] <- \hlfunctioncall{paste0}(lookup$taxon[i], \hlstring{"-aggregated"})
        lookup$match[i] <- \hlstring{"aggregated"}
    \}
\}
lookup
\end{alltt}
\begin{verbatim}
                     taxon                    traits      match
1         gammarus roeseli                  gammarus      genus
2        gammarus tigrinus                  gammarus      genus
3           coenagrionidae coenagrionidae-aggregated aggregated
4 potamopyrgus antipodarum  potamopyrgus antipodarum     direct
5                    xxxxx                      <NA>       <NA>
\end{verbatim}
\end{kframe}
\end{knitrout}

Finally we have only one taxon left - clearly an error. We remove this from our dataset:
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
abundances <- abundances[!abundances$taxon == lookup$taxon[\hlfunctioncall{is.na}(lookup$traits)], 
    ]
\end{alltt}
\end{kframe}
\end{knitrout}

No we can create \emph{species x sites} and \emph{traits x species} matrices, which could be plugged into methods to analyse trait responses \citep{kleyer_assessing_2012}.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# species (as matched with trait table) by site matrix}
abundances$traits_taxa <- lookup$traits[\hlfunctioncall{match}(\hlfunctioncall{tolower}(abundances$taxon), lookup$taxon)]

\hlfunctioncall{require}(reshape2)
\hlcomment{# reshape data to long format and name rows by samples}
L <- \hlfunctioncall{dcast}(abundances, sample ~ traits_taxa, fun.aggregate = sum, value.var = \hlstring{"abundance"})
\hlfunctioncall{rownames}(L) <- L$sample
L$sample <- NULL
L
\end{alltt}
\begin{verbatim}
  coenagrionidae-aggregated gammarus potamopyrgus antipodarum
1                        10       12                       10
2                         6       14                        0
\end{verbatim}
\begin{alltt}

\hlcomment{# traits by species matrix}
Q <- traits[, 2:7][\hlfunctioncall{match}(\hlfunctioncall{names}(L), traits$taxon_cleaned), ]
\hlfunctioncall{rownames}(Q) <- Q$taxon_cleaned
Q$taxon_cleaned <- NULL
Q
\end{alltt}
\begin{verbatim}
                          T1M1 T1M2 T1M3 T2M1 T2M2
coenagrionidae-aggregated    0    0    1    3    1
gammarus                     0    0    3    1    3
potamopyrgus antipodarum     1    0    3    1    3
\end{verbatim}
\begin{alltt}

\hlcomment{# check}
\hlfunctioncall{all}(\hlfunctioncall{rownames}(Q) == \hlfunctioncall{colnames}(L))
\end{alltt}
\begin{verbatim}
[1] TRUE
\end{verbatim}
\end{kframe}
\end{knitrout}

This is just an example how taxonomic APIs (via taxize) could be used to search for matches up- and downwards the taxonomic ladder. We are looking forward to integrate the freshwaterecology.info database \citep{freshwaterecology} into taxize, which will facilitate trait-based analyses in R.

\end{appendices}

\bibliographystyle{eco_lett}
\bibliography{refs}

>>>>

\documentclass[10pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

@@

\usepackage{alltt}

% amsmath package, useful for mathematical formulas
\usepackage{amsmath}
% amssymb package, useful for mathematical symbols
\usepackage{amssymb}

% graphicx package, useful for including eps and pdf graphics
% include graphics with the command \includegraphics
\usepackage{graphicx}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}
\usepackage{color}

% Use doublespacing - comment out for single spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\topmargin 0.0cm
\oddsidemargin 0.5cm
\evensidemargin 0.5cm
\textwidth 16cm 
\textheight 21cm

% Bold the 'Figure #' in the caption and separate it with a period
% Captions will be left justified
\usepackage[labelfont=bf,labelsep=period,justification=raggedright]{caption}

% Use the PLoS provided bibtex style
\bibliographystyle{plos2009}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

\pagestyle{myheadings}
%% ** EDIT HERE **
%% ** EDIT HERE **
%% PLEASE INCLUDE ALL MACROS BELOW
\usepackage{hyperref}
\usepackage{array}
%% END MACROS SECTION
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

@@

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# The tnrs function accepts a vector of 1 or more}
splist_tnrs <- \hlfunctioncall{tnrs}(query = splist, getpost = \hlstring{"POST"}, source_ = \hlstring{"iPlant_TNRS"})
\end{alltt}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Calling http://taxosaurus.org/retrieve/7763b460ecdf76eee52f78e9569e7c91}}\begin{alltt}

\hlcomment{# Remove some fields}
(splist_tnrs <- splist_tnrs[, !\hlfunctioncall{names}(splist_tnrs) %in% \hlfunctioncall{c}(\hlstring{"matchedName"}, \hlstring{"annotations"}, 
    \hlstring{"uri"})])
\end{alltt}
\begin{verbatim}
##            submittedName         acceptedName    sourceId score
## 3       Helanthus annuus    Helianthus annuus iPlant_TNRS  0.98
## 1         Pinos contorta       Pinus contorta iPlant_TNRS  0.96
## 4  Collomia grandiflorra Collomia grandiflora iPlant_TNRS  0.99
## 5       Abies magnificaa      Abies magnifica iPlant_TNRS  0.98
## 10       Rosa california     Rosa californica iPlant_TNRS  0.99
## 9         Datura wrighti      Datura wrightii iPlant_TNRS  0.98
## 7       Mimulus bicolour      Mimulus bicolor iPlant_TNRS  0.98
## 8       Nicotiana glauca     Nicotiana glauca iPlant_TNRS     1
## 6          Maddia sativa         Madia sativa iPlant_TNRS  0.97
## 2    Bartlettia scapposa   Bartlettia scaposa iPlant_TNRS  0.98
\end{verbatim}
\begin{alltt}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
tsns <- \hlfunctioncall{get_tsn}(searchterm = splist, searchtype = \hlstring{"sciname"}, verbose = FALSE)
comnames <- \hlfunctioncall{lapply}(tsns, getcommonnamesfromtsn)
\end{alltt}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getCommonNamesFromTSN?tsn=36616\\\#\# http://www.itis.gov/ITISWebService/services/ITISService/getCommonNamesFromTSN?tsn=183327\\\#\# http://www.itis.gov/ITISWebService/services/ITISService/getCommonNamesFromTSN?tsn=31037\\\#\# http://www.itis.gov/ITISWebService/services/ITISService/getCommonNamesFromTSN?tsn=181834\\\#\# http://www.itis.gov/ITISWebService/services/ITISService/getCommonNamesFromTSN?tsn=24818\\\#\# http://www.itis.gov/ITISWebService/services/ITISService/getCommonNamesFromTSN?tsn=30521\\\#\# http://www.itis.gov/ITISWebService/services/ITISService/getCommonNamesFromTSN?tsn=33245\\\#\# http://www.itis.gov/ITISWebService/services/ITISService/getCommonNamesFromTSN?tsn=30574\\\#\# http://www.itis.gov/ITISWebService/services/ITISService/getCommonNamesFromTSN?tsn=38040\\\#\# http://www.itis.gov/ITISWebService/services/ITISService/getCommonNamesFromTSN?tsn=36822}}\begin{alltt}

\hlcomment{# Unfortunately, common names are not standardized like species names, so}
\hlcomment{# there are multiple common names for each taxon}
\hlfunctioncall{sapply}(comnames, length)
\end{alltt}
\begin{verbatim}
##  [1] 3 3 3 3 3 3 3 3 3 3
\end{verbatim}
\begin{alltt}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# As we already have Taxonomic Serial Numbers from ITIS, let's just get}
\hlcomment{# classifications from ITIS. Note that we could use uBio instead.}
class_list <- \hlfunctioncall{classification}(tsns)
\end{alltt}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getFullHierarchyFromTSN?tsn=36616\\\#\# http://www.itis.gov/ITISWebService/services/ITISService/getFullHierarchyFromTSN?tsn=183327\\\#\# http://www.itis.gov/ITISWebService/services/ITISService/getFullHierarchyFromTSN?tsn=31037\\\#\# http://www.itis.gov/ITISWebService/services/ITISService/getFullHierarchyFromTSN?tsn=181834\\\#\# http://www.itis.gov/ITISWebService/services/ITISService/getFullHierarchyFromTSN?tsn=24818\\\#\# http://www.itis.gov/ITISWebService/services/ITISService/getFullHierarchyFromTSN?tsn=30521\\\#\# http://www.itis.gov/ITISWebService/services/ITISService/getFullHierarchyFromTSN?tsn=33245\\\#\# http://www.itis.gov/ITISWebService/services/ITISService/getFullHierarchyFromTSN?tsn=30574\\\#\# http://www.itis.gov/ITISWebService/services/ITISService/getFullHierarchyFromTSN?tsn=38040\\\#\# http://www.itis.gov/ITISWebService/services/ITISService/getFullHierarchyFromTSN?tsn=36822}}\begin{alltt}
\hlfunctioncall{sapply}(class_list, nrow)
\end{alltt}
\begin{verbatim}
##  [1] 12 11 12 11 12 12 12 12 12 12
\end{verbatim}
\begin{alltt}

@@

\begin{figure}[!h] 
\centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# Fetch phylogeny from phylomatic}
phylogeny <- \hlfunctioncall{phylomatic_tree}(taxa = \hlfunctioncall{as.character}(allnames$spname), taxnames = TRUE, 
    get = \hlstring{"POST"}, informat = \hlstring{"newick"}, method = \hlstring{"phylomatic"}, storedtree = \hlstring{"R20120829"}, 
    taxaformat = \hlstring{"slashpath"}, outformat = \hlstring{"newick"}, clean = \hlstring{"true"}, parallel = TRUE)
\end{alltt}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: No parallel backend registered\\\#\# Warning: executing \%dopar\% sequentially: no parallel backend registered}}\begin{alltt}
\hlcomment{# Format teeth-labels}
phylogeny$tip.label <- \hlfunctioncall{capwords}(phylogeny$tip.label, onlyfirst = TRUE)
\hlcomment{# plot phylogeny}
\hlfunctioncall{plot}(phylogeny)
\end{alltt}
\end{kframe}
\includegraphics[width=4in,height=4in]{figure/phylogeny1}

\includegraphics[width=4in,height=4in]{figure/phylogeny2}

@@

\hlcomment{# Make a map}
p <- \hlfunctioncall{gbifmap}(occurr_list) + \hlfunctioncall{guides}(col = \hlfunctioncall{guide_legend}(title = \hlstring{""}, nrow = 3, 
    byrow = TRUE)) + \hlfunctioncall{theme}(legend.position = \hlstring{"bottom"}, legend.key = \hlfunctioncall{element_blank}()) + 
    \hlfunctioncall{coord_equal}()
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: could not find function "gbifmap"}}\begin{alltt}
p
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'p' not found}}\end{kframe}
\end{knitrout}
